Scattering from compact objects: \\ Regge poles and the Complex Angular Momentum method

### 2019-12-21 rainbowCAM.tex
some minor changes to appendix

\moh{I have established some proprieties (symmetry relations) to connect different quadrants and I moved part of the paragraph from section III-c to the appendix.  Sam \& Tom : Please be critical and It is free to change.}

In this appendix, we will show that, for $\omega$ real, the zeros of the $S$-matrix (\textit{i.e.}, the Regge poles), or in other words
the zeros of the coefficient $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~\eqref{Matrix_S_CAM}]
\begin{equation}\label{zeros_Am}
   A^{(-)}_{\lambda-1/2} (\omega)\Big{|}_{\lambda =\lambda_n} = 0
\end{equation}
are lying in the right-half of the complex $\lambda$-plan. To do this, it is convenient to write the boundary conditions \eqref{bc_1_in} and \eqref{bc_2_in} in the following form:
\begin{equation}
\label{bc_CAM}
\phi_{\lambda-\frac{1}{2}}(\omega) \sim
\left\{
\begin{aligned}
&r^{\lambda+\frac{1}{2}}\hspace{8em} \scriptstyle{r \rightarrow 0,} \quad \text{(regular solution)}\\
&A_{\lambda-1/2}^{(-)}(\omega) e^{-i\omega r_*} + A_{\lambda-1/2}^{(+)}(\omega) e^{+i\omega r_*}  \hspace{0.2em}\scriptstyle{r_* \rightarrow +\infty.}
\end{aligned}
\right.
\end{equation}

Let us consider the radial equation~\eqref{H_Radial_equation}, written for the regular solution
\begin{equation}\label{Wave_equation_reg}
   \frac{d^2}{dr_*^2}\phi_{\omega,\lambda-1/2}(r)+\left(\omega^2 -V_{\lambda-1/2}\right) \phi_{\omega,\lambda-1/2}(r) =0
 \end{equation}
and its complex conjugate
 \begin{equation}\label{Wave_equation_reg_conjugate}
   \frac{d^2}{dr_*^2}\phi^*_{\omega,\lambda-1/2}(r)+ \left(\omega^2 -V_{\lambda^*-1/2}\right)\phi^*_{\omega,{\lambda-1/2}}(r) =0
 \end{equation}
Multiplying \eqref{Wave_equation_reg} by $\phi^*_{\omega,\lambda-1/2}(r)$ and \eqref{Wave_equation_reg_conjugate} by $\phi_{\omega,\lambda-1/2}(r)$ and subtracting, it follows,
\begin{widetext}
\begin{equation}\label{Derivative_Wronskian}
\begin{aligned}
 \phi^*_{\omega,\lambda-1/2}(r) \frac{d^2}{dr_*^2}\phi_{\omega,\lambda-1/2}(r) - \phi_{\omega,\lambda-1/2}(r) \frac{d^2}{dr_*^2} \phi^*_{\omega,\lambda-1/2}(r) &= 2 i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{2\text{Re}[\lambda]\text{Im}[\lambda]}{r^2} \\
                           &= 2 i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{\text{Im}[\lambda^2]}{r^2}
 \end{aligned}
\end{equation}
\end{widetext}
In Eq.~\eqref{Derivative_Wronskian}, the l.h.s is the derivative of the Wronskian, $W$, of the two solutions respect to $r_*$ and it is a constant (\textit{i.e.}, $d/dr_* W[\phi^*,\phi] = 0$) if $\lambda$ either real or purely imaginary. According to Eq.~\eqref{Derivative_Wronskian}, we can write
\begin{equation}\label{Derivative_Wronskian_bis}
\frac{d}{dr_*}W[\phi^*,\phi]= 2i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{2\text{Re}[\lambda]\text{Im}[\lambda]}{r^2}
\end{equation}

Integration of \eqref{Derivative_Wronskian_bis} gives
\begin{equation}\label{Evaluation_W}
\lim_{r_*\rightarrow \infty}  W[\phi^*,\phi] = 4i\, \text{Im}[\lambda]\, \text{Re}[\lambda] \int_{0}^{+\infty} \frac{|\phi_{\lambda-1/2}(\omega)|^2}{r^2}\,dr
\end{equation}
where we have used $\frac{dr}{dr_*}=f(r)$ to transform the integration variable. In other hand,  By evaluating the  Wronskian from the boundary condition~\eqref{bc_CAM}, we obtain
\begin{equation}\label{Evaluation_W_bis}
\lim_{r_*\rightarrow \infty}  W[\phi^*,\phi] =-2i\, \omega\left(|A^{(-)}_{\lambda-1/2}|^2-|A^{(+)}_{\lambda-1/2}|^2\right)
\end{equation}
hence we get (\textit{c.f.} \eqref{Evaluation_W} and  \eqref{Evaluation_W_bis})
\begin{equation}\label{Evaluation_W_bis_1}
  |A^{(-)}_{\lambda-1/2}|^2-|A^{(+)}_{\lambda-1/2}|^2 = -\frac{2}{\omega}\text{Re}[\lambda]\text{Im}[\lambda]\int_{0}^{+\infty} \frac{ |\phi_{\lambda-1/2}(\omega)|^2}{r^2}\,dr
\end{equation}

@@

It is important to note that we have, under transformation $\omega \rightarrow -\omega$, the coefficient $A^{(-)}_{\lambda-1/2}(\omega)$ defined by the problem  \eqref{H_Radial_equation}--\eqref{bc_1_in}--\eqref{bc_2_in}, satisfy the symmetry relation
\begin{equation}\label{symmetry_relation}
 A^{(-)}_{\lambda-1/2}(-\omega) = \left[A^{(-)}_{\lambda^*-1/2}(\omega)\right]^*
\end{equation}
where, we have
\begin{equation}\label{Relation_1st_4th}
\lambda_n(-\omega) = \lambda_n(\omega)^*
\end{equation}

>>>>

\moh{I have established some proprieties (symmetry relations) to connect different quadrants and I moved part of the paragraph from section III-c to the appendix.  Sam \& Tom : Please be critical and It is free to change.}
\tom{I have made a few minor rewordings. Agree with moving III C para to here.}.

In this appendix, we will show that, for $\omega$ real, the zeros of the $S$-matrix (\textit{i.e.}, the Regge poles), or in other words
the zeros of the coefficient $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~\eqref{Matrix_S_CAM}]
\begin{equation}\label{zeros_Am}
   A^{(-)}_{\lambda-1/2} (\omega)\Big{|}_{\lambda =\lambda_n} = 0
\end{equation}
are lying in the right-half of the complex $\lambda$-plan.

\tom{ rewording: In this appendix we will show which quadrants of the complex $\lambda$-plane may contain the Regge poles for scalar and axial metric perturbations on a stellar background. In other words, we will constrain the possible locations of the zeros of the coefficient $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~\eqref{Matrix_S_CAM}],
\begin{equation}\label{zeros_Am}
   A^{(-)}_{\lambda-1/2} (\omega)\Big{|}_{\lambda =\lambda_n} = 0,
\end{equation}
for $\omega$ real.
}

To do this, it is convenient to write the boundary conditions \eqref{bc_1_in} and \eqref{bc_2_in} in the following form:
\begin{equation}
\label{bc_CAM}
\phi_{\lambda-\frac{1}{2}}(\omega) \sim
\left\{
\begin{aligned}
&r^{\lambda+\frac{1}{2}}\hspace{8em} \scriptstyle{r \rightarrow 0,} \quad \text{(regular solution)}\\
&A_{\lambda-1/2}^{(-)}(\omega) e^{-i\omega r_*} + A_{\lambda-1/2}^{(+)}(\omega) e^{+i\omega r_*}  \hspace{0.2em}\scriptstyle{r_* \rightarrow +\infty.}
\end{aligned}
\right.
\end{equation}

Let us consider the radial equation~\eqref{H_Radial_equation}, written for the regular solution
\begin{equation}\label{Wave_equation_reg}
   \frac{d^2}{dr_*^2}\phi_{\omega,\lambda-1/2}(r)+\left(\omega^2 -V_{\lambda-1/2}\right) \phi_{\omega,\lambda-1/2}(r) =0
 \end{equation}
and its complex conjugate
 \begin{equation}\label{Wave_equation_reg_conjugate}
   \frac{d^2}{dr_*^2}\phi^*_{\omega,\lambda-1/2}(r)+ \left(\omega^2 -V_{\lambda^*-1/2}\right)\phi^*_{\omega,{\lambda-1/2}}(r) =0
 \end{equation}
Multiplying \eqref{Wave_equation_reg} by $\phi^*_{\omega,\lambda-1/2}(r)$ and \eqref{Wave_equation_reg_conjugate} by $\phi_{\omega,\lambda-1/2}(r)$ and subtracting, it follows that
\begin{widetext}
\begin{equation}\label{Derivative_Wronskian}
\begin{aligned}
 \phi^*_{\omega,\lambda-1/2}(r) \frac{d^2}{dr_*^2}\phi_{\omega,\lambda-1/2}(r) - \phi_{\omega,\lambda-1/2}(r) \frac{d^2}{dr_*^2} \phi^*_{\omega,\lambda-1/2}(r) &= 2 i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{2\text{Re}[\lambda]\text{Im}[\lambda]}{r^2} \\
                           &= 2 i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{\text{Im}[\lambda^2]}{r^2}
 \end{aligned}
\end{equation}
\end{widetext}
The LHS of Eq.~\eqref{Derivative_Wronskian} is the derivative of the Wronskian, $W$, of the two solutions with respect to $r_*$ and it is a constant (\textit{i.e.}, $d/dr_* W[\phi^*,\phi] = 0$) if $\lambda$ either real or purely imaginary. According to Eq.~\eqref{Derivative_Wronskian}, we can write
\begin{equation}\label{Derivative_Wronskian_bis}
\frac{d}{dr_*}W[\phi^*,\phi]= 2i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{2\text{Re}[\lambda]\text{Im}[\lambda]}{r^2}.
\end{equation}

Integration of \eqref{Derivative_Wronskian_bis} gives
\begin{equation}\label{Evaluation_W}
\lim_{r_*\rightarrow \infty}  W[\phi^*,\phi] = 4i\, \text{Im}[\lambda]\, \text{Re}[\lambda] \int_{0}^{+\infty} \frac{|\phi_{\lambda-1/2}(\omega)|^2}{r^2}\,dr
\end{equation}
where we have used $\frac{dr}{dr_*}=f(r)$ to transform the integration variable. On the other hand,  by evaluating the  Wronskian from the boundary condition~\eqref{bc_CAM}, we obtain
\begin{equation}\label{Evaluation_W_bis}
\lim_{r_*\rightarrow \infty}  W[\phi^*,\phi] =-2i\, \omega\left(|A^{(-)}_{\lambda-1/2}|^2-|A^{(+)}_{\lambda-1/2}|^2\right),
\end{equation}
hence we get (\textit{c.f.} \eqref{Evaluation_W} and  \eqref{Evaluation_W_bis})
\begin{equation}\label{Evaluation_W_bis_1}
  |A^{(-)}_{\lambda-1/2}|^2-|A^{(+)}_{\lambda-1/2}|^2 = -\frac{2}{\omega}\text{Re}[\lambda]\text{Im}[\lambda]\int_{0}^{+\infty} \frac{ |\phi_{\lambda-1/2}(\omega)|^2}{r^2}\,dr.
\end{equation}

@@

It is important to note that under the transformation $\omega \rightarrow -\omega$, the coefficient $A^{(-)}_{\lambda-1/2}(\omega)$ defined by \eqref{H_Radial_equation}--\eqref{bc_1_in}--\eqref{bc_2_in} satisfies the symmetry relation
\begin{equation}\label{symmetry_relation}
 A^{(-)}_{\lambda-1/2}(-\omega) = \left[A^{(-)}_{\lambda^*-1/2}(\omega)\right]^*,
\end{equation}
and thus
\begin{equation}\label{Relation_1st_4th}
\lambda_n(-\omega) = \lambda_n(\omega)^*.
\end{equation}
